Fixing Vulnerabilities Hinders Maintainability

### 2019-01-30 paper/ICPC19/icpc19.tex
discussion
more things on intro

In this paper, we present the results of our analysis on the maintainability of 607 security changes collected from open-source software.

The main contributions of the present work is:
\begin{itemize}
	\item An empirical study on the impact of security changes on software maintainability and what patterns need more attention.
	\item A software package with all scripts and data created to perform the empirical evaluation, for reproducibility. Available here: $<url>$.

>>>>

The particular subject of this paper is to explore whether there is a trade-off
between refactoring source code to fix identified vulnerabilities while keeping
(or even improving) the maintainability of the software system. In other words,
we are interested in answering the following overarching question

\begin{framed}
\noindent
Does improving security have a negative impact on code
maintainability?
\end{framed}

\noindent
In this paper, we present the results of our analysis on the maintainability of
607 security changes collected from open-source software.

The main contributions of the present work is:
\begin{itemize}
	\item An empirical study on the impact of security changes on software
	maintainability and what patterns need more attention.

  \item An analysis of how likely energy changes need to be
  maintained, in comparison to regular commits.

	\item A replication package with all scripts and data created to perform the
	empirical evaluation, for reproducibility. Available here: $<url>$.
